Labour Market Resilience

### 2024-03-12 outputs/paper/paper.qmd
update appendix

## Survey Introduction
The supplemental survey is available here: [Google Form Link](https://forms.gle/Ffma5ggEcP6wfumu6)

@@

## Survey Questions
\begin{itemize}
        \item Demographic Information:
            \begin{enumerate}
                \item What is your age group?
                \begin{itemize}
                  \item Under 18
                  \item 18-24
                  \item 25-34
                  \item 35-44
                  \item 45-54
                  \item 55-64
                  \item 65+
                \end{itemize}
                \item What is your highest level of education?
                \begin{itemize}
                  \item High school graduate
                  \item Bachelor's degree
                  \item Graduate or professional degree
                \end{itemize}
                \item Please specify your gender:
                \begin{itemize}
                  \item Male
                  \item Female
                  \item Non-binary
                  \item Prefer not to say
                \end{itemize}
            \end{enumerate}
        \item Employment Status and Industry:
              \begin{enumerate}
                \item What is your current employment status?
                \begin{itemize}
                  \item Employed full-time
                  \item Employed part-time
                  \item Unemployed
                  \item Retired
                  \item Student
                \end{itemize}
                \item If employed, what industry do you work in?
                \begin{itemize}
                  \item Manufacturing
                  \item Construction
                  \item Retail
                  \item Hospitality
                  \item Healthcare
                  \item Education
                  \item Information Technology
                  \item Professional Services
                  \item Other (please specify)
                \end{itemize}
            \end{enumerate}
        \item Impact of Economic Downturns:
              \begin{enumerate}
                \item How did the 2008 financial crisis and/or the COVID-19 pandemic affect your working hours? Did your hours:
                \begin{itemize}
                  \item Increase
                  \item Decrease
                  \item Stay the same
                  \item Not applicable/I wasn't employed during these times
                \end{itemize}
                \item Did you have to switch to remote work during the COVID-19 pandemic?
                \begin{itemize}
                  \item Yes
                  \item No
                  \item Not applicable
                \end{itemize}
              \end{enumerate}
        \item Responses to Economic Downturns:
              \begin{enumerate}
                \item In times of economic downturn, what support measures do you believe are most effective for workers?
                \begin{itemize}
                  \item Unemployment benefits
                  \item Skills retraining programs
                  \item Direct financial aid
                  \item Flexible work arrangements
                  \item Other (please specify)
                \end{itemize}
            \end{enumerate}
\end{itemize}

\newpage
# References

>>>>

## Survey Introduction

The supplemental survey is available here: [Google Form Link](https://forms.gle/Ffma5ggEcP6wfumu6)

@@

## Survey Questions

\begin{itemize}
        \item Demographic Information:
            \begin{enumerate}
                \item What is your age group?
                \begin{itemize}
                  \item Under 18
                  \item 18-24
                  \item 25-34
                  \item 35-44
                  \item 45-54
                  \item 55-64
                  \item 65+
                \end{itemize}
                \item What is your highest level of education?
                \begin{itemize}
                  \item High school graduate
                  \item Bachelor's degree
                  \item Graduate or professional degree
                \end{itemize}
                \item Please specify your gender:
                \begin{itemize}
                  \item Male
                  \item Female
                  \item Non-binary
                  \item Prefer not to say
                \end{itemize}
            \end{enumerate}
        \item Employment Status and Industry:
              \begin{enumerate}
                \item What is your current employment status?
                \begin{itemize}
                  \item Employed full-time
                  \item Employed part-time
                  \item Unemployed
                  \item Retired
                  \item Student
                \end{itemize}
                \item If employed, what industry do you work in?
                \begin{itemize}
                  \item Manufacturing
                  \item Construction
                  \item Retail
                  \item Hospitality
                  \item Healthcare
                  \item Education
                  \item Information Technology
                  \item Professional Services
                  \item Other (please specify)
                \end{itemize}
            \end{enumerate}
        \item Impact of Economic Downturns:
              \begin{enumerate}
                \item How did the 2008 financial crisis and/or the COVID-19 pandemic affect your working hours? Did your hours:
                \begin{itemize}
                  \item Increase
                  \item Decrease
                  \item Stay the same
                  \item Not applicable/I wasn't employed during these times
                \end{itemize}
                \item Did you have to switch to remote work during the COVID-19 pandemic?
                \begin{itemize}
                  \item Yes
                  \item No
                  \item Not applicable
                \end{itemize}
              \end{enumerate}
        \item Responses to Economic Downturns:
              \begin{enumerate}
                \item In times of economic downturn, what support measures do you believe are most effective for workers?
                \begin{itemize}
                  \item Unemployment benefits
                  \item Skills retraining programs
                  \item Direct financial aid
                  \item Flexible work arrangements
                  \item Other (please specify)
                \end{itemize}
            \end{enumerate}
\end{itemize}

## Survey Completion Message

Thank you for participating in our survey. Your insights are invaluable to our ongoing research into labour market dynamics and the effects of economic downturns on working hours. Your contribution helps us identify areas for targeted interventions and policy recommendations to support vulnerable labour market groups.
\newpage
# References
